% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\author{}
\date{}

\begin{document}

Software Requirements Specification

for

Jeevan Rakshak

Version 1.0 approved

Prepared by Aditya,Deepak,Siddiq and Anshaj

Indian Institute of Information Technology Ranchi

1 April 2023

Table of Contents

\textbf{Table of Contents 0}

1. Introduction \protect\hyperlink{introduction}{1}

1.1 Purpose \protect\hyperlink{purpose}{1}

1.2 Product Scope \protect\hyperlink{__RefHeading___Toc441230974}{1}

1.3 Definitions. Acronyms, and Abbreviations
\protect\hyperlink{__RefHeading___Toc441230975}{1}

1.4 References \protect\hyperlink{product-scope}{1}

1.5 Overview
\protect\hyperlink{definitions.-acronyms-and-abbreviations}{1}

2. Overall Description \protect\hyperlink{overall-description}{2}

2.1 Product Perspective \protect\hyperlink{product-perspective}{2}

2.2 Product Functions \protect\hyperlink{product-functions}{2}

2.3 User Characteristics \protect\hyperlink{user-characteristics}{2}

2.4 Constraints 3

2.5 Assumptions and Dependencies 3

3. Specific Requirements 4

3.1 External Interface Requirements 4

3.2 Functional Requirements 4

3.3 Performance Requirements 4

3.4 Logical Database Requirements 4

3.5 Design Constraints 5

4. Other Nonfunctional Requirements 6

4.1 Performance Requirements 6

4.2 Compatibility Requirements 6

4.3 Security Requirements 6

4.4 Accessibility Requirements 6

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

\hypertarget{purpose}{%
\subsection{\texorpdfstring{Purpose }{Purpose }}\label{purpose}}

The purpose of this document is to provide a detailed description of the
requirements for the development of a web and Mobile application and
that displays information on government health schemes. The web
application will be built using React and will connect to a Firebase
Realtime Database and Mobile App will be built using Flutter and Dart
and It will also connect with a same Firebase Realtime Database as web
Application. It will provide features such as user login, user
registration, filtering of schemes by age, name and government, and a
FAQ section. The purpose of this application is to make the information
about the government health schemes more accessible to the public. This
will help people to make informed decisions and choose the best health
scheme that suits their needs.

\hypertarget{product-scope}{%
\subsection{Product Scope}\label{product-scope}}

The scope of this project is to develop a web and Mobile application
that will display information about the various government health
schemes in different states. The both application will allow users to
search for health schemes based on their state and other criteria. The
both application will also provide details about the eligibility
criteria, benefits, and other relevant information about the schemes as
well as include an FAQ system for queries.It is for the common users as
well as advanced users aiding in their form filling.

\hypertarget{definitions.-acronyms-and-abbreviations}{%
\subsection{Definitions. Acronyms, and
Abbreviations}\label{definitions.-acronyms-and-abbreviations}}

Web App refers to a website that a user can use.

React refers to a popular frontend library of Javascript.

Flutter refers to a frontend of mobile App for cross Platform.

Firebase refers to a server hosting and managing platform by Google.

Realtime Database refers to a Firebase database feature.

\hypertarget{references}{%
\subsection{References}\label{references}}

IEEE standard template for IEEE standard

\hypertarget{overview}{%
\subsection{Overview}\label{overview}}

This document is organized into Introduction, Overall Description,
Specific Requirements System features and Other non functional
Requirements. Each individual section is further subdivided into bullets
describing their respective content.

\hypertarget{overall-description}{%
\section{Overall Description}\label{overall-description}}

\hypertarget{product-perspective}{%
\subsection{Product Perspective}\label{product-perspective}}

The web and Mobile Application is a standalone app and should be
designed to be accessible to all users, regardless of their level of
technical expertise or familiarity with government health schemes.

The app should also be designed to be scalable and flexible so that it
can be easily updated as new health schemes are introduced or existing
schemes are modified. It should be able to handle large amounts of data
and provide users with real-time updates on the status of their
applications.

In addition, the app should be designed with security in mind, with
appropriate measures in place to protect user data and prevent
unauthorized access.

\hypertarget{product-functions}{%
\subsection{Product Functions}\label{product-functions}}

A government health scheme display web app and Mobile app should have
several functions that make it easy for users to access information
about various health schemes offered by the government. Some of these
functions include:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Eligibility check: The app should allow users to check their
  eligibility for different health schemes based on their demographic,
  income, social details, etc\emph{.}
\item
  Scheme discovery: The app should help users find relevant health
  schemes from hundreds of schemes available based on their
  eligibility\emph{.}
\item
  Application guidance: The app should guide users on how to apply for
  different government health schemes\emph{.}
\item
  Dedicated scheme page: The app should provide a dedicated scheme page
  with detailed knowledge, FAQs, and application process\emph{.}
\item
  User-friendly interface: The app should be designed to be
  user-friendly and accessible to all users, regardless of their level
  of technical expertise or familiarity with government health
  schemes\emph{.}
\item
  Scalability and flexibility: The app should be scalable and flexible
  so that it can be easily updated as new health schemes are introduced
  or existing schemes are modified\emph{.}
\item
  Security: The app should be designed with security in mind, with
  appropriate measures in place to protect user data and prevent
  unauthorized access\emph{.}
\end{enumerate}

\hypertarget{user-characteristics}{%
\subsection{User Characteristics}\label{user-characteristics}}

User classes for a government health scheme display web and Mobile app
can be divided into two categories:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Registered users: These are users who have created an account on the
  app and can access additional features such as personalized scheme
  recommendations, personalized filtering, etc
\item
  Unregistered users: These are users who have not created an account on
  the app and can only access basic features such as scheme discovery
  and eligibility check.
\item
  Administrators: Those who can edit schemes and add new entries to
  database along with answering queries
\end{enumerate}

\hypertarget{constraints}{%
\subsection{Constraints}\label{constraints}}

This web app needs to work on all major web browsers on all major OS and
should be responsive as well as fast and Mobile App needs to work on all
cross platform like android, iOS and web.

This web and Mobile app needs to be also easy to understand and secure.

\hypertarget{assumptions-and-dependencies}{%
\subsection{Assumptions and
Dependencies}\label{assumptions-and-dependencies}}

One major dependency is the availability of data along with the govt
websites and Mobile App that provide them. These need to be verified and
up to date at all times, also we will be assuming those websites and
Mobile App to display correct information regarding the schemes as
verifying that is out of scope for this platform.

\hypertarget{specific-requirements}{%
\section{Specific Requirements}\label{specific-requirements}}

\hypertarget{external-interface-requirements}{%
\subsection{External Interface
Requirements}\label{external-interface-requirements}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  User interface: The app should have an intuitive and user-friendly
  interface that allows users to easily navigate and access information.
\item
  Hardware interfaces: The app should be compatible with different
  hardware devices such as smartphones, tablets, and computers.
\item
  Data interfaces: The app should be able to access and retrieve data
  from backend database.
\item
  Security interfaces: The app should be designed with security in mind
  to protect sensitive data such as patient information.
\end{enumerate}

\hypertarget{functional-requirements}{%
\subsection{Functional Requirements}\label{functional-requirements}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  User Registration: The application should allow users to register and
  create an account.
\item
  User Login: The application should allow registered users to log in
  and access the information.
\item
  Search: The application should provide a search option to allow users
  to search for schemes based on their state, eligibility criteria,
  benefits, etc.
\item
  Scheme Details: The application should display details about the
  health schemes, including eligibility criteria, benefits, and other
  relevant information.
\item
  Eligibility criteria: The app should provide information about
  eligibility criteria for different health schemes.
\item
  Application process: The app should provide information about the
  application process for different health schemes.
\item
  FAQ section: The app should provide a page to ask queries and view
  previously answered queries
\end{enumerate}

\hypertarget{performance-requirements}{%
\subsection{Performance Requirements}\label{performance-requirements}}

The app should respond to the user without much delay while running on
web and Mobile and fetching the data from the backend firebase server.
It should also be able to post data as questions fast enough as well as
so auth.

\hypertarget{logical-database-requirements}{%
\subsection{Logical Database
Requirements}\label{logical-database-requirements}}

On a high level this app should use a get request for fetching data from
firebase server as a json object about schemes with a specific schema to
display as cards. It should use a post request for questions and a
mixture of get and post requests for user authentication

\hypertarget{design-constraints}{%
\subsection{Design Constraints}\label{design-constraints}}

The app should be responsive across all screen sizes and support all the
old and latest version of smart phone as well as be able to run on all
major browsers

\hypertarget{section}{%
\section{\texorpdfstring{\hfill\break
}{ }}\label{section}}

\hypertarget{other-nonfunctional-requirements}{%
\section{Other Nonfunctional
Requirements}\label{other-nonfunctional-requirements}}

\hypertarget{performance-requirements-1}{%
\subsection{Performance Requirements}\label{performance-requirements-1}}

The app should respond to the user without much delay while running on
web and Mobile and fetching the data from the backend firebase server.
It should also be able to post data as questions fast enough as well as
so auth.

\hypertarget{compatibility-requirements}{%
\subsection{Compatibility
Requirements}\label{compatibility-requirements}}

The app should be compatible with all major browsers and OS and Smart
Phones. It should also support all standard network protocols for
opening and maintaining a safe and reliable connection to the database.

\hypertarget{security-requirements}{%
\subsection{Security Requirements}\label{security-requirements}}

The app should keep user or patient data private and only show a user
recommendations based on their data.

\hypertarget{accessibility-requirements}{%
\subsection{Accessibility
Requirements}\label{accessibility-requirements}}

The app should have a simple and intuitive UI with more focus on
graphics and less of heavy technical terminology since it has to reach
common masses

\end{document}
